---
title: "Poland Analysis Code"
output: pdf_document
date: "2024-01-16"
---


```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
library(sandwich)
library(lmtest)
library(kableExtra)
library(scales)
source("/Users/ashleyblum/Documents/Work/Research/ScaleReduce.R")
```

```{r load, include=FALSE}

load("/Users/ashleyblum/Google Drive/Poland_Media/dat.RData")

load("/Users/ashleyblum/Google Drive/Poland_Media/dat_long.RData")

#excerpt_topics <- read.csv("/Users/ashleyblum/Documents/Work/Research/Source Branding and Foreign Affairs/excerpt_topics.csv")
#load("/Users/ashleyblum/Documents/Work/Research/Source Branding and Foreign Affairs/text_dat_branding.RData")


"%notin%" <- function(x, y) !(x %in% y)


```

# Intro

These are the preliminary results from our Survey in December 2023. Our first set of analyses, conducted on the trial level, concern the trust index. The index is measured on a scale from 0 to 1 with higher values indicating higher trust. 


The trust index is the mean of the following items on a 0 to 1 scale: 
\begin{align*}
\text{Untrustworthy} ----&--- \text{Trustworthy}\\
\text{Misleading} ----&--- \text{Truthful}\\
\text{Biased} ----&--- \text{Objective}\\
\end{align*} 

# Preliminary Summary Stats

## Sample demographics and survey responses

```{r}
dat <- dat %>%
  mutate(party = case_when(voted == 1 & party_voted %notin% c("forgot") ~ party_voted,
                      voted == 0 ~ party_supported))
summary_dat <- dat %>%
  summarise(
    female = mean(female, na.rm = T),
    age = mean(age, na.rm = T),
    ba_grad = mean(ba_grad, na.rm = T),
    full_time = mean(employment == "Working full time"),
    part_time = mean(employment == "Working part time"),
    retired = mean(employment == "Retired"),
    voted = mean(voted),
    PiS = sum(party %in% "pis") / nrow(dat),
    Dem_Opposition = sum(party %in% c("ko", "nl", "td"))  / nrow(dat),
    Confederation = sum(party %in% "kon") / nrow(dat),
    political_interest = mean(pol_interest_n),
    tvp_watcher = mean(use_tvp, na.rm =  T),
    tvn_watcher = mean(use_tvn, na.rm = T)
  )%>%
  t() %>%
  as_tibble()


demovars <- c("Female", "Age",  "BA Graduate",
              "Employed Full Time", "Employed Part Time", "Retired",
              "Voted", "PiS", "Democratic Opposition", "Confederation",
              "Political Interest", "TVP Watcher", "TVN Watcher")

summary_dat <- tibble(demovars, summary_dat)
```

```{r, results='asis'}
print(xtable::xtable(summary_dat, caption = "Summary Statistics"), include.rownames = F, caption.placement = "top")


```




## Blind Condition Outcome Mean by Party and Source
```{r response_summaries_blind, include=FALSE}
party_summary <- dat_long %>%
  filter(treatment == "blind") %>%
  group_by(pro_pis) %>%
  summarise(
    trust_index = mean(trust_index, na.rm = T),
    trustworthy = mean(trustworthy, na.rm = T),
    truthful = mean(truthful, na.rm = T),
    objective = mean(objective, na.rm = T)
    ) %>% 
  mutate_if(is.numeric, round, digits = 2)


source_summary <- dat_long %>%
  filter(treatment == "blind") %>%
  group_by(source) %>%
  summarise(
    trust_index = mean(trust_index, na.rm = T),
    trustworthy = mean(trustworthy, na.rm = T),
    truthful = mean(truthful, na.rm = T),
    objective = mean(objective, na.rm = T)
    ) %>% 
  mutate_if(is.numeric, round, digits = 2)


```

```{r print_response_summaries, echo=FALSE, results='asis'}
kable(party_summary)
kable(source_summary)
```

```{r}
#Std. Dev Trust Index
sd(dat_long$trust_index, na.rm = T)

```

## Distribution of the Outcome Variable

```{r hist_trust, echo=FALSE}
hist(dat_long$trust_index, xlab = "Trust Index", main = "Histogram of Trust Index", breaks = 30)
```
`

```{r dist_trustworthy, echo=FALSE}
barplot(prop.table(table(dat_long$trustworthy)), xlab = "Trustworthy", ylab = "Proportion", main = "Distribution of 'Trustworthy'",
        col = "steelblue", border = "black", width = 0.6, names.arg = c("0", ".17", ".33", ".5", ".67", ".83", "1"))
```

```{r dist_objective, echo=FALSE}
barplot(prop.table(table(dat_long$objective)), xlab = "Objective", ylab = "Proportion", main = "Distribution of 'Objective'",
        col = "steelblue", border = "black", width = 0.6, names.arg = c("0", ".17", ".33", ".5", ".67", ".83", "1"))
```

```{r dist_truthful, echo=FALSE}
barplot(prop.table(table(dat_long$truthful)), xlab = "Truthful/Misleading", ylab = "Proportion", main = "Distribution of 'Truthful/Misleading'",
        col = "steelblue", border = "black", width = 0.6, names.arg = c("0", ".17", ".33", ".5", ".67", ".83", "1"))
```


\clearpage

# Main Source Cue Effects

These are the main results from our test of the source cue effect. In all cases, we are comparing responses in the blind condition to responses in the revealed condition, conditional on source. As pre-specified, we fit separate models for respondents that voted/would have voted for PiS and respondents that voted/would have voted for parties in the Democratic Opposition coalition. Note that Poland has a multi-party system 

Here is the code for fitting the models. Note that for each we fit an OLS model on treated with excerpt fixed effects. Standard errors are clustered on respondent. 

```{r fit_main, message=FALSE}

dat_long <- dat_long %>%
  mutate(treated = case_when(treatment == "blind" ~ 0,
                             treatment == "revealed" ~ 1))

dat <- dat %>%
  mutate(treated = case_when(treatment == "blind" ~ 0,
                             treatment == "revealed" ~ 1))

#fit main models, OLS

#note I'll be using p for pro-pis and d for Democratic Opposition
 

#TVP effect on pro-pis
m1_p_tvp <- lm(trust_index ~ treated + excerpt,
              data = dat_long[dat_long$pro_pis == 1 &
                                dat_long$source == "tvp",])
m1_p_tvp_cl <- coeftest(m1_p_tvp, vcov = vcovCL, cluster = ~ResponseId)



#TVN effect on anti-pis
m1_d_tvn <- lm(trust_index ~ treated + excerpt,
              data = dat_long[dat_long$anti_pis == 1 &
                                dat_long$source == "tvn",])
m1_d_tvn_cl <- coeftest(m1_d_tvn, vcov = vcovCL, cluster = ~ResponseId)


#TVN effect on pro-pis
m1_p_tvn <- lm(trust_index ~ treated + excerpt,
              data = dat_long[dat_long$pro_pis == 1 &
                                dat_long$source == "tvn",])
m1_p_tvn_cl <- coeftest(m1_p_tvn, vcov = vcovCL, cluster = ~ResponseId)



#tvp effect on anti-pis
m1_d_tvp <- lm(trust_index ~ treated + excerpt,
              data = dat_long[dat_long$anti_pis == 1 &
                                dat_long$source == "tvp",])
m1_d_tvp_cl <- coeftest(m1_d_tvp, vcov = vcovCL, cluster = ~ResponseId)
```


\clearpage

The results can be found in Table \ref{tab:main1}. We see that, consistent with our hypotheses, the TVP brand has a positive effect on trust for those who support the PiS party but it has a negative effect on trust for those who supported the opposition coalition. By contrast, the TVN brand has a negative effective on trust for those who support the PiS party but a positive effect on those who support the opposition. The negative effect of TVP for the opposition supporters is especially strong. 

```{r print_main_results, results='asis', message=FALSE, echo=FALSE}
m1 <- m1_p_tvp
m2 <- m1_p_tvn
m3 <- m1_d_tvp
m4 <- m1_d_tvn

m1_cl <- m1_p_tvp_cl
m2_cl <- m1_p_tvn_cl
m3_cl <- m1_d_tvp_cl
m4_cl <- m1_d_tvn_cl

  
additional_lines <- c("Excerpt FE", rep("Yes", 4))

stargazer::stargazer(m1, m2, m3, m4,
                     header = FALSE,
                     label = "tab:main1", 
                     title = "Main Source Effect Results",
                     covariate.labels = c("SourceRevealed"),
                     dep.var.labels = c("Trust Index"),
                     column.labels = c("TVP|PiS", "TVN|PiS",  "TVP|DO", "TVN|DO"),
                     se=list(m1_cl[,2], m2_cl[,2], m3_cl[,2], m4_cl[,2]),
                     omit.stat = c("f", "rsq", "ser"),
                     omit = c("excerpt", "Constant"),
                     add.lines = list(additional_lines), 
                     notes = "Trust index measured on 0 (low trust) to 1 (high trust)")
```

```{r cohens_counter}
#Effect Size, Counter Source
g0_counter <- na.omit(dat_long$trust_index[dat_long$counter_source == 1 &
                                             dat_long$treated == 0])
g1_counter <- na.omit(dat_long$trust_index[dat_long$counter_source == 1 &
                                             dat_long$treated == 1])

mean(g0_counter)
mean(g1_counter)
dim_counter <- mean(g1_counter) - mean(g0_counter) #calc dif in means
dim_counter

#dif in means as percentage of control mean
dim_counter / mean(g0_counter, na.rm = T)

sd_pooled_counter <- effectsize::sd_pooled(g0_counter, g1_counter)
dim_counter / sd_pooled_counter

##use packages to calculate cohen's d
cohensD_counter <- effsize::cohen.d(g0_counter, g1_counter) #calc cohens d with effsize packages
cohensD_counter
```

```{r cohens_aligned}
#Effect Size Aligned Source
##control aligned trials - aligned
g0_aligned <- na.omit(dat_long$trust_index[dat_long$aligned_source == 1 &
                                             dat_long$treated == 0])
##treated aligned trials - aligne
g1_aligned <- na.omit(dat_long$trust_index[dat_long$aligned_source == 1 &
                                             dat_long$treated == 1])

mean(g0_aligned) 
mean(g1_aligned)
dim_aligned <- mean(g1_aligned) - mean(g0_aligned) #calc aligend dif in means
dim_aligned
#aligned dif in means as percentage of control mean
dim_aligned / mean(g0_aligned)


cohensD_aligned <- effsize::cohen.d(g0_aligned, g1_aligned) #calc cohens d with effsize packages
cohensD_aligned
```

```{r cohens_pis}
#Effect Size, Split By Party

##PiS Supporters - TVN effect

g0_p_tvn <- na.omit(dat_long$trust_index[dat_long$pro_pis == 1 &
                                           dat_long$source == "tvn" &
                                           dat_long$treated == 0])
g1_p_tvn <- na.omit(dat_long$trust_index[dat_long$pro_pis == 1 &
                                           dat_long$source == "tvn" &
                                           dat_long$treated == 1])

mean(g0_p_tvn)
mean(g1_p_tvn)

dim_rep_tvn <- mean(g1_p_tvn) - mean(g0_p_tvn) #dif in means
dim_rep_tvn
sd_pooled_rep_tvn <- effectsize::sd_pooled(g0_p_tvn, g1_p_tvn) #pooled sd
dim_rep_tvn / sd_pooled_rep_tvn #cohens d manual

cohensD_rep_tvn <- effsize::cohen.d(g0_p_tvn, g1_p_tvn) #calc cohens d with effsize packages
cohensD_rep_tvn
```

```{r cohens_dem_opposition}
##Opposition - tvp Effect

g0_d_tvp <- na.omit(dat_long$trust_index[dat_long$anti_pis == 1 &
                                           dat_long$source == "tvp" &
                                           dat_long$treated == 0])
g1_d_tvp <- na.omit(dat_long$trust_index[dat_long$anti_pis == 1 &
                                           dat_long$source == "tvp" &
                                           dat_long$treated == 1])

mean(g0_d_tvp)
mean(g1_d_tvp)

dim_d_tvp <- mean(g1_d_tvp) - mean(g0_d_tvp) #dif in means
sd_pooled_d_tvp <- effectsize::sd_pooled(g0_d_tvp, g1_d_tvp) #pooled sd
dim_d_tvp / sd_pooled_d_tvp #cohens d manual


cohensD_d_tvp <- effsize::cohen.d(g0_d_tvp, g1_d_tvp) #calc cohens d with effsize packages
cohensD_d_tvp
```
\clearpage

# Blind Taste Test


First we will look at content-based preferences separately for each of our 3 topic groups. These analyses use only the blind condition responses. We ask whether pro-PiS respondents prefer TVP to TVN, even without knowing its source. Note: I use m_btt to refer to blind taste test models
```{r fit_btt}
#preference for TVP content blind, general topic, pro-pis
m_btt_p_gen <- lm(trust_index ~ I(source == "tvp"), data = dat_long[dat_long$treatment == "blind"
                                                                    & dat_long$pro_pis == 1
                                                                    & dat_long$topic == "general",])
m_btt_p_gen_cl <- coeftest(m_btt_p_gen, vcov = vcovCL, cluster = ~ResponseId)

#preference for TVP content blind, general topic, anti-pis
m_btt_d_gen <- lm(trust_index ~ I(source == "tvp"), data = dat_long[dat_long$treatment == "blind"
                                                                    & dat_long$anti_pis == 1
                                                                    & dat_long$topic == "general",])
m_btt_d_gen_cl <- coeftest(m_btt_d_gen, vcov = vcovCL, cluster = ~ResponseId)


#preference for TVP content blind, outsiders topic, pro-pis
m_btt_p_out <- lm(trust_index ~ I(source == "tvp"), data = dat_long[dat_long$treatment == "blind"
                                                                    & dat_long$pro_pis == 1
                                                                    & dat_long$topic == "outsiders",])
m_btt_p_out_cl <- coeftest(m_btt_p_out, vcov = vcovCL, cluster = ~ResponseId)

#preference for TVP content blind, outsiders topic, anti-pis
m_btt_d_out <- lm(trust_index ~ I(source == "tvp"), data = dat_long[dat_long$treatment == "blind"
                                                                    & dat_long$anti_pis == 1
                                                                    & dat_long$topic == "outsiders",])
m_btt_d_out_cl <- coeftest(m_btt_d_out, vcov = vcovCL, cluster = ~ResponseId)


#preference for TVP content blind, politics topic, pro-pis
m_btt_p_pol <- lm(trust_index ~ I(source == "tvp"), data = dat_long[dat_long$treatment == "blind"
                                                                    & dat_long$pro_pis == 1
                                                                    & dat_long$topic == "politics",])
m_btt_p_pol_cl <- coeftest(m_btt_p_pol, vcov = vcovCL, cluster = ~ResponseId)

#preference for TVP content blind, politics topic, anti-pis
m_btt_d_pol <- lm(trust_index ~ I(source == "tvp"), data = dat_long[dat_long$treatment == "blind"
                                                                    & dat_long$anti_pis == 1
                                                                    & dat_long$topic == "politics",])
m_btt_d_pol_cl <- coeftest(m_btt_d_pol, vcov = vcovCL, cluster = ~ResponseId)
```


```{r print_btt_results, results='asis', message=FALSE, echo=FALSE}
m1 <- m_btt_p_gen
m2 <- m_btt_p_out
m3 <- m_btt_p_pol

m1_cl <- m_btt_p_gen_cl
m2_cl <- m_btt_p_out_cl
m3_cl <- m_btt_p_pol_cl


additional_lines <- c("Excerpt FE", rep("Yes", 4))

stargazer::stargazer(m1, m2, m3,
                     header = FALSE,
                     label = "tab:btt_pis", 
                     title = "Blind Source Preferences: Pro-PiS",
                     covariate.labels = c("TVP"),
                     dep.var.labels = c("Trust Index"),
                     column.labels = c("General", "Globalization",  "Politics"),
                     se=list(m1_cl[,2], m2_cl[,2], m3_cl[,2]),
                     omit.stat = c("f", "rsq", "ser"),
                     add.lines = list(additional_lines), 
                     notes = "Trust index measured on 0 (low trust) to 1 (high trust)")


m1 <- m_btt_d_gen
m2 <- m_btt_d_out
m3 <- m_btt_d_pol

m1_cl <- m_btt_d_gen_cl
m2_cl <- m_btt_d_out_cl
m3_cl <- m_btt_d_pol_cl


additional_lines <- c("Excerpt FE", rep("Yes", 4))

stargazer::stargazer(m1, m2, m3,
                     header = FALSE,
                     label = "tab:btt_pis", 
                     title = "Blind Source Preferences: Anti-PiS",
                     covariate.labels = c("TVP"),
                     dep.var.labels = c("Trust Index"),
                     column.labels = c("General", "Globalization",  "Politics"),
                     se=list(m1_cl[,2], m2_cl[,2], m3_cl[,2]),
                     omit.stat = c("f", "rsq", "ser"),
                     add.lines = list(additional_lines), 
                     notes = "Trust index measured on 0 (low trust) to 1 (high trust)")
```


#Exposure effects on attitudes

#distribution of measures
```{r}
hist(dat$outsider_threat)
hist(dat$oppo_distrust)
```


```{r}
plot(density((dat$outsider_threat[dat$pro_pis == 1])), col="blue", main = "Outsider Threat, By Party")
lines(density((dat$outsider_threat[dat$anti_pis == 1])), col="orange")
```
```{r}
plot(density((dat$oppo_distrust[dat$pro_pis == 1])), col="blue", main = "DO Distrust, By Party")
lines(density((dat$oppo_distrust[dat$anti_pis == 1])), col="orange")
```

2nd Order Beliefs 

```{r}
hist(dat$m_outsider_threat)
hist(dat$m_oppo_distrust)
```


```{r}
plot(density((dat$m_outsider_threat[dat$pro_pis == 1])), col="blue", main = "Meta Perceptions: Outsider Threat, By Party")
lines(density((dat$m_outsider_threat[dat$anti_pis == 1])), col="orange")
```
```{r}
plot(density((dat$m_oppo_distrust[dat$pro_pis == 1])), col="blue", main = "Meta Perceptions: DO Distrust, By Party")
lines(density((dat$m_oppo_distrust[dat$anti_pis == 1])), col="orange")
```

## ANOVAs for control and treatment conditions 
Compares control conditions, i.e., pure control and TVN source with any topic (general, on-topic, and off-topic) both for blind and revealed conditions; and treatment conditions, i.e.,
TVP source with on-topic topics and both blind and revealed conditions.

```{r}
library(dplyr)
#options(scipen = 999)

load("dat.RData")

# create condition var for ANOVA
dat <- dat %>%
  mutate(condition = as.factor(case_when(
    articles == 1 ~ (paste0(source, "_", treatment, "_", topic)),
    articles == 0 ~ "pure_control")), 
    pro_pis = as.factor(pro_pis))
```

### DV: outsider threat

#### Control conditions

```{r}
aov_outsider_control <- aov(data = dat %>% filter(condition == "pure_control" | source == "tvn"),
               outsider_threat ~ condition * pro_pis)
summary(aov_outsider_control) # party main effect
tukey_outsider_control <- TukeyHSD(aov_outsider_control)
tukey_outsider_control_df <- as.data.frame(tukey_outsider_control[[3]]) %>%
  arrange(`p adj`)
#print(tukey_outsider_control_df) # differences only for pro-pis and anti-pis respondents
```

#### Treatment conditions
```{r}
aov_outsider_treatment <- aov(data = dat %>% filter(source == "tvp" & topic == "outsiders"),
                    outsider_threat ~ condition * pro_pis)
summary(aov_outsider_treatment) # party main effect only
tukey_outsider_treatment <- TukeyHSD(aov_outsider_treatment)
tukey_outsider_treatment_df <- as.data.frame(tukey_outsider_treatment[[3]]) %>%
  arrange(`p adj`)
#print(tukey_outsider_treatment_df)
```

### DV: democratic opposition distrust

#### Control conditions
```{r}
aov_opposition_control <- aov(data = dat %>% filter(condition == "pure_control" | source == "tvn"),
                              oppo_distrust ~ condition * pro_pis)
summary(aov_opposition_control) # party main effect
tukey_opposition_control <- TukeyHSD(aov_opposition_control)
tukey_opposition_control_df <- as.data.frame(tukey_opposition_control[[3]]) %>%
  arrange(`p adj`)
#print(tukey_opposition_control_df) # differences only for pro-pis and anti-pis respondents
```

#### Treatment conditions
```{r}
aov_opposition_treatment <- aov(data = dat %>% filter(source == "tvp" & topic == "politics"),
                                oppo_distrust ~ condition * pro_pis)
summary(aov_opposition_treatment) # party main effect only
tukey_opposition_treatment <- TukeyHSD(aov_opposition_treatment)
tukey_opposition_treatment_df <- as.data.frame(tukey_opposition_treatment[[3]]) %>%
  arrange(`p adj`)
#print(tukey_opposition_treatment_df)
```

### DV: meta-perception of outsider threat

#### Control conditions
```{r}
aov_m_outsider_control <- aov(data = dat %>% filter(condition == "pure_control" | source == "tvn"),
                              m_outsider_threat ~ condition * pro_pis)
summary(aov_m_outsider_control) # party main effect
tukey_m_outsider_control <- TukeyHSD(aov_m_outsider_control)
tukey_m_outsider_control_df <- as.data.frame(tukey_m_outsider_control[[3]]) %>%
  arrange(`p adj`)
#print(tukey_m_outsider_control_df) # differences only for pro-pis and anti-pis respondents
```

#### Treatment conditions
```{r}
aov_m_outsider_treatment <- aov(data = dat %>% filter(source == "tvp" & topic == "outsiders"),
                                m_outsider_threat ~ condition * pro_pis)
summary(aov_m_outsider_treatment) # party main effect only
tukey_m_outsider_treatment <- TukeyHSD(aov_m_outsider_treatment)
tukey_m_outsider_treatment_df <- as.data.frame(tukey_m_outsider_treatment[[3]]) %>%
  arrange(`p adj`)
#print(tukey_m_outsider_treatment_df)
```

### DV: meta-perception of democratic opposition distrust

#### Control conditions
```{r}
aov_m_opposition_control <- aov(data = dat %>% filter(condition == "pure_control" | source == "tvn"),
                                m_oppo_distrust ~ condition * pro_pis)
summary(aov_m_opposition_control) # party main effect
tukey_m_opposition_control <- TukeyHSD(aov_m_opposition_control)
tukey_m_opposition_control_df <- as.data.frame(tukey_m_opposition_control[[3]]) %>%
  arrange(`p adj`)
#print(tukey_m_opposition_control_df) # differences only for pro-pis and anti-pis respondents
```

#### Treatment conditions
```{r}
aov_m_opposition_treatment <- aov(data = dat %>% filter(source == "tvp" & topic == "politics"),
                                  m_oppo_distrust ~ condition * pro_pis)
summary(aov_m_opposition_treatment) # party main effect only
tukey_m_opposition_treatment <- TukeyHSD(aov_m_opposition_treatment)
tukey_m_opposition_treatment_df <- as.data.frame(tukey_m_opposition_treatment[[3]]) %>%
  arrange(`p adj`)
#print(tukey_m_opposition_treatment_df)
```

### DV: preference for inter-party cooperation

#### Control conditions
```{r}
aov_coop_control <- aov(data = dat %>% filter(condition == "pure_control" | source == "tvn"),
                        party_coop ~ condition * pro_pis)
summary(aov_coop_control) # party main effect
tukey_coop_control <- TukeyHSD(aov_coop_control)
tukey_coop_control_df <- as.data.frame(tukey_coop_control[[3]]) %>%
  arrange(`p adj`)
#print(tukey_coop_control_df) # only 14 significant comparisons (for other analyzes abour 43)
```

#### Treatment conditions
```{r}
aov_coop_treatment <- aov(data = dat %>% filter(source == "tvp" & topic == "politics"),
                          party_coop ~ condition * pro_pis)
summary(aov_coop_treatment) # party main effect only
tukey_coop_treatment <- TukeyHSD(aov_coop_treatment)
tukey_coop_treatment_df <- as.data.frame(tukey_coop_treatment[[3]]) %>%
  arrange(`p adj`)
#print(tukey_coop_treatment_df) # only 3 significant differences (for other analyzes 4)
```

## Treatment Effects

```{r}
dat <- dat %>%
  mutate(outsider_treated = case_when(
    articles == 0 ~ 0,
    source == "tvn" ~ 0,
    source == "tvp" & topic == "outsiders" ~ 1
  ))

m_outsider_int <- lm(outsider_threat ~ outsider_treated * pro_pis, data = dat) 
m_outsider_p <- lm(outsider_threat ~ outsider_treated, data = dat[dat$pro_pis == 1,]) 
m_outsider_d <- lm(outsider_threat ~ outsider_treated, data = dat[dat$anti_pis == 1,]) 

```

```{r}
dat <- dat %>%
  mutate(politics_treated = case_when(
    articles == 0 ~ 0,
    source == "tvn" ~ 0,
    source == "tvp" & topic == "politics" ~ 1
  ))

m_politics_int <- lm(oppo_distrust ~ politics_treated * pro_pis, data = dat) 
m_politics_p <- lm(oppo_distrust ~ politics_treated, data = dat[dat$pro_pis == 1,]) 
m_politics_d <- lm(oppo_distrust ~ politics_treated, data = dat[dat$anti_pis == 1,]) 

```



